Capstone Movielens Report

### 2025-12-07 reports/capstone-movielens.site/02.7.UMGYE-model.Rmd
Report section updated: UMGYE Model Building.

#### [train_UMGY_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L74) Function {#func.train_UMGY_effect}
\

This function is used to train the current model using the _Train Set_ dataset passed in the `train_set` parameter.
The following is the source code of the function:
```{r eval=FALSE}
train_UMGY_effect <- function(train_set, lambda = 0){
  if (is.na(lambda)) {
    stop("Function: train_UMGY_effect
`lambda` is `NA`")
  }

  train_set |>
    calc_date_general_effect(lambda) |>
    calc_UMGY_effect()
}

::: {.noteblock data-latex=""}
The source code of the [train_UMGY_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L74) function is also available in the [UMGYE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L1) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L74) script on _GitHub_.
:::

##### Return

A data structure containing information about _User+Movie+Genre+Year (UMGY) Effect_.

#### [train_UMGY_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L84) Function {#func.train_UMGY_effect.cv}
\

This function is used to train the current model using the _5-Fold Cross Validation_.
The following is the source code of the function:
```{r eval=FALSE}
train_UMGY_effect.cv <- function(lambda = 0){
  if (is.na(lambda)) {
    stop("Function: train_UMGY_effect.cv
`lambda` is `NA`")
  }

  calc_date_general_effect.cv(lambda) |> calc_UMGY_effect()  
}
```

::: {.noteblock data-latex=""}
The source code of the [train_UMGY_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L84) function is also available in the [UMGYE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L1) section of the [UMGY-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L84) script on _GitHub_.
:::

##### Return

A data structure containing information about _User+Movie+Genre+Year (UMGY) Effect_.

@@

::: {.noteblock data-latex=""}
In the code snippet above, we use the [train_UMGY_effect.cv](#func.train_UMGY_effect.cv) function described in section [UMGYE Model: Utility Functions] of [Appendix A: Support Functions] to *This Report*.
:::

We can now construct predictors and calculate the _RMSE_ of the current model using the [calc_UMGY_effect_RMSE.cv](#func.calc_UMGY_effect_RMSE.cv) function described above:

@@

RMSEs.ResultTibble.UMGYE <- RMSEs.ResultTibble.rglr.UMGE |> 
  RMSEs.AddRow("UMGYE Model", 
               cv.UMGY_effect.RMSE,
               comment = "User+Movie+Genre+Year Effect (UMGYE) Model")
```
```{r}
RMSE_kable(RMSEs.ResultTibble.UMGYE)
```

>>>>

@@

We can now construct predictors and calculate the *RMSE* of the current model as shown in the code snippet below:

@@

::: {.noteblock data-latex=""}
In the code snippets above, we use the [train_UMGY_effect.cv](#func.train_UMGY_effect.cv) and [calc_UMGY_effect_RMSE.cv](#func.calc_UMGY_effect_RMSE.cv) functions described in the [UMGYE Model: Utility Functions] section of [Appendix A: Support Functions] to *This Report*.
:::

```{r, eval=FALSE}
RMSEs.ResultTibble.UMGYE <- RMSEs.ResultTibble.rglr.UMGE |> 
  RMSEs.AddRow("UMGYE Model", 
               cv.UMGY_effect.RMSE,
               comment = "User+Movie+Genre+Year Effect (UMGYE) Model")
```
```{r}
RMSE_kable(RMSEs.ResultTibble.UMGYE)
```
